More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-05-23 2016-Weak-FH-Bisim/WeakBisim.tex
Definition 7

\begin{definition}[Operational semantics of open pNets]
	\label{def:operationalSemantics}
	The semantics of a pNet $\pNet$ is an open automaton $A\!= 
	<\!\!Holes(\pNet),States(\pNet),InitState(\pNet),
	\mathcal{T}\!\!>$ where $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
%	\begin{itemize}
%		\item $J$ is the set of holes: $Holes(p)= J$. 
		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
%		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
%		\item $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
%	\end{itemize}

>>>>

\begin{definition}[Operational semantics of open pNets]
	\label{def:operationalSemantics}
	The semantics of a pNet, $\pNet$ is an open automaton $A\!= 
	<\!\!Holes(\pNet),States(\pNet),InitState(\pNet),\mathcal{T}\!\!>$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the following  rules:
%	\begin{itemize}
%		\item $J$ is the set of holes: $Holes(p)= J$. 
		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
%		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
%		\item $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
%	\end{itemize}
